### 2017-02-12 section/3_redundancy.tex
address reviewer concerns

{\color{red} We calculate the redundancy for one input instruction $I$ by using 1 to subtract the normalized
edit-distance between the two sequences of values returned by $I$ in the two
loop instances, denoted by $SeqA$ and $SeqB$. 
The exact formula is the following:
}
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

>>>>

{\color{red}
We calculate the redundancy for an input instruction $I$ based on the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances
and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
The intuition is that the redundancy rate should be 1 if one sequence is the 
sub-sequence of the other; and, the redundancy rate should be 0 if these two
sequences are completely different.
}
The exact formula is the following:
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

### 2017-02-12 section/5_exper.tex
address review-1
roll back some of my updates
address reviewer concerns

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler benchmark suite~\cite{Alabama, toddlerbuglist}.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of them.
Due to the focus of Toddler, all of these bugs are caused by inefficient
\textit{nested} loops and only cover two types of inefficiency root causes,
as shown in the bottom half of Table \ref{tab:benchmarks}.
We extract these bugs and re-implemented them in 
C/C++;
we re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. Each extracted benchmark contains at least five
loops, except for two cases with four loops each.

@@

To evaluate the coverage, accuracy, and performance of \Tool, we mainly conduct
three sets of evaluation. First, we apply \Tool to the real root-cause loop to
see if \Tool can correctly identify the root-cause category and suggest
a fix strategy. Second, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. Third, we evaluate the run-time performance of
applying \Tool to the real root-cause loop.

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns). 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that match what developers took in practice
for 33 out of \allbugs cases.

@@

%\input section/tab_top5

As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 0 real
false positive and 22 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

Here, benign false positives mean that \Tool analysis result is true ---
some loops are indeed cross-iteration/loop redundant or indeed producing
results in only a tiny portion of loop iterations. However, those
problems are \textit{not} fixed by developers in their performance patches.

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 20 out of the
22 benign cases. % 11 out of 13 in the first benchmark set 
In fact, this is not a problem for \Tool in 
real usage scenarios, because statistical debugging or profiling can often
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. 
We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
%the current diagnosis results are obtained by running the
%program only \textbf{once} under the problem-triggering workload.
%If we use sparser sampling, more failure runs will be needed to obtain good
%diagnosis results.

>>>>

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler benchmark suite~\cite{Alabama, toddlerbuglist}.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of them.
Due to the focus of Toddler, all of these bugs are caused by inefficient
\textit{nested} loops and only cover two types of inefficiency root causes,
as shown in the bottom half of Table \ref{tab:benchmarks}.
We extract these bugs and re-implemented them in 
C/C++;
we re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. Each extracted benchmark contains at least five
loops, except for two cases with four loops each.
%{\color{red} All re-implemented benchmarks used in our experiments are released on github~\cite{re-implemented}.}

@@

@@

{\color{red}
\noindent\textbf{Research questions to answer}
We mainly conduct three sets of evaluation to answer three key research 
questions regarding the coverage, accuracy, and performance of \Tool,

\textbf{RQ1}.
Can \Tool correctly identify inefficiency categories and suggest fix 
strategies for many real-world loops? (Sec.\ref{sec:coverage})

\textbf{RQ2}.
Might \Tool report many false positives and hence waste developers' diagnosis
effort? (Sec.\ref{sec:result_acc})

\textbf{RQ3}.
What is the run-time overhead of \Tool? (Sec.\ref{sec:result_perf})
}

\subsection{Coverage Results}
\label{sec:coverage}
{\color{red}
To answer \textbf{RQ1}, we apply \Tool to real root-cause loops to see if 
it can accurately identify inefficiency categories.
As shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns), 
\Tool does provide good diagnosis coverage.
}
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that match what developers took in practice
for 33 out of \allbugs cases.

@@

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. 
}
{\color{red}
As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having 2 real
false positive and 20 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

%TODO for Linhai: 
%1. check the accuracy of the next two paragraphs
%2. fill in the XXX and XXX in the next paragraph
%3. change the false positive numbers in Table
%4. change the true false positive and benign false positive numbers in other part of the paper

The two real false positives happen for benchmarks XXX and XXX.
These two loops are identified as
redundant and resultless by \Tool. However, they
are very difficult to fix and hence are not changed in the patches.
Since these two loops are ranked higher than the true positive loops by
statistical debugging, they could cost (waste) \Tool users some effort during 
performance diagnosis. Future work could try to prune these false positives
by estimating the fix difficulty.

\Tool also reports 20 benign false positives.
In these cases, \Tool correctly identified truly inefficient loops.
However, these loops are not the main contributors to the 
performance problems perceived by the users, and hence are not
fixed in patches. 
Different from the two false positives discussed above, these 20 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}

@@

{\color{red}
To answer \textbf{RQ3}, we evaluate the run-time performance of
applying \Tool to the real root-cause loop. 
}
As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. 
We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
%the current diagnosis results are obtained by running the
%program only \textbf{once} under the problem-triggering workload.
%If we use sparser sampling, more failure runs will be needed to obtain good
%diagnosis results.

### 2017-02-12 section/evaltax.tex
address reviewer concerns

{\color{red} Our previous} work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler suite in C/C++;
(4) Mozilla suite, including Firefox web browser and Thunderbird
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
{\color{red} We manually inspected randomly sampled bug reports and identified 
65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study 
here.

>>>>

Our previous work \cite{PerfBug,SongOOPSLA2014} studied the on-line bug
databases of five representative open-source software projects:
(1) Apache suite, including HTTPD web server written in C/C++,
TomCat server written in Java, and Ant build management tool in Java;
(2) Chromium Google Chrome browser in C/C++;
(3) GCC compiler suite in C/C++;
(4) Mozilla suite, including Firefox web browser and Thunderbird
Email client in C/C++ and JavaScript; 
(5) MySQL database server in C/C++.
{\color{red} By manually inspecting a set of randomly sampled bug reports,
previous work identified 
65 performance problems that are perceived and reported by users~\cite{SongOOPSLA2014}.}  
Among these 65 problems, 45 problems are related to inefficient loops and 
hence are the target of the study
here.
